---
title: "Assignment 2"
author: "Payal Sen"
date: "1/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE, warning=FALSE)

```

## GitHub User Description and User Page URL
Mike Slinn - Avid scala and Play Framework user & developer. According to his bio on Github he is a "Voyager of inner space". Mike is the founder of Micronautics Research Corporation. He has has sixty-two (193) repos and fifty-five (69) followers. Mike Slinn’s GitHub page url https://github.com/mslinn.

Set github token

```{r}
my_token = "154dd284f7b8c8a2f8eb3ca8804c13896fac4af6"
Sys.setenv(GITHUB_TOKEN = my_token)
```

Libraries used
```{r library}
#devtools::install_github("r-lib/gh")
library(httr)
library(devtools)
library(gh)
library(tidyverse)
library(curl)
library (purrr)
library (doParallel)
library(knitr)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(stringr)
library(RColorBrewer)
library(ggthemes)

```

## User's Basic Information

* In the code below, data for user **mslinn** is read from github api. This list format data is the stored in  **user**.   
* List data is extracted into a dataframe **user_df** 

```{r user}

user <- gh("/users/mslinn", .limit = Inf)

user_df <- data.frame(user_id = user$id,user_name = user$name,
             pub_repos = user$public_repos, followers = user$followers)

kable(user_df,caption = "This table shows the user's id, name, public_repos, followers") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left",
                fixed_thead = T)  
                
```

## Followers’ Basic Information

* In the code below, followers data is read from github api. This list format data is  stored in **user_followers**.   
* Using **map_df**, all follower data was extracted and a dataframe was created with the same name i.e. **user_followers**. 
* **Map()** function used to get the user details of each follower.
* Lastly a For loop is run to capture the id, name, public_repos, followers for each follower.
* For some followers name is not blank, they have been replaced by **"NA"**

```{r followers}

user_followers <- gh("/users/mslinn/followers", .limit = Inf)

user_followers = map_df(
  user_followers, magrittr::extract, names(user_followers[[1]]))

followers_details = 
  map(user_followers$login, ~gh(paste0("/users/", .)))

followers_df = NULL

for (i in seq_along(followers_details)){
  id <- followers_details[[i]]$id
  public_repos <- followers_details[[i]]$public_repos
  followers <- followers_details[[i]]$followers
  if (is.null(followers_details[[i]]$name)){
    name = "NA"
    }
  else{
    name = followers_details[[i]]$name
    }
  followers_df = rbind(followers_df, data.frame(id, name, public_repos, followers))
}


kable(followers_df,
      caption = "This table summarizes followers’ id, name, public_repos and followers.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left",
                fixed_thead = T)
```

## User's Repositories Information
* In the code below, repository data is read from github api. This list format data is  stored in **user_repos**.   
* For loop is run to capture the name, language, size, forks_count,      stargazers_count, watchers_count and open_issues_count for each repository.
* For repositories with language as null, it is replaced with **"Unknown"**.

```{r repos}

user_repos <- gh("/users/mslinn/repos", .limit = Inf)

repos_df = NULL

for (i in seq_along(user_repos)){
  name <- user_repos[[i]]$name
  size <- user_repos[[i]]$size
  forks_count <- user_repos[[i]]$forks_count
  stargazers_count <- user_repos[[i]]$stargazers_count
  watchers_count <- user_repos[[i]]$watchers_count
  open_issues_count <- user_repos[[i]]$open_issues_count
  if (is.null(user_repos[[i]]$language)){
    language = "Unknown"
  }
  else{
    language = user_repos[[i]]$language
  }
  repos_df = rbind(repos_df, data.frame(name,language,size,forks_count,stargazers_count,
                                  watchers_count,open_issues_count))
}

kable(repos_df,
      caption = "This table summarizes the repositories' name, language, size, forks_count,      stargazers_count, watchers_count, open_issues_count") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left",
                fixed_thead = T)
    

```
## Summary of Issues by Repository
* Issue data is read from user repository and stored in dataframe **mslinn_repos_df**
* For loop is run to capture the total no. of open and closed issues within each repository, and also to calculate the average duration for an issue to close.

```{r issues}

mslinn_repos_df <-
  data_frame(
    repo = user_repos %>% map_chr("name"),
    issue = repo %>%
     map(~ gh(repo = .x, endpoint = "/repos/mslinn/:repo/issues?state=all",.limit = #Inf)
                )
                ))

issue_df = NULL


for(i in 1:length(mslinn_repos_df$issue)){
  open = 0
  closed = 0
  duration = 0
  if(length(mslinn_repos_df$issue[[i]])>0){
    for(j in 1:length(mslinn_repos_df[[2]][[i]]))
      if(mslinn_repos_df[[2]][[i]][[j]][["state"]]=='open'){
        open = open+1
      }else{
        closed = closed+1
        duration = duration + ymd_hms(mslinn_repos_df[[2]][[i]][[j]][["closed_at"]]) - ymd_hms(mslinn_repos_df[[2]][[i]][[j]][["created_at"]])
      }
  }
  duration = duration / closed
  duration = as.duration(duration)
  repo = mslinn_repos_df$repo[[i]]
  issue_df = rbind(issue_df, data.frame(repo,open,closed,duration))
}

kable(issue_df,
      caption = "This table summarizes the issues and include columns: repo name, the number of open issues, the number of closed issues, the average duration to close an issue") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left",
                fixed_thead = T)
```

## Plots

### Plot1- shows Mike's followers with more than 100 public_repos and their followers.

```{r plot1}

# 
plot1 <- ggplot(followers_df%>% filter(public_repos>100) %>% filter(name != 'NA') , aes(x=followers, y=name))+
  geom_point()+
  labs(title="Name of followers VS their follower")+
  xlab("Name")+
  ylab("Followers")

plot1
```

### Plot2- summarizes open issues in each of Mike's repositories.

```{r plot2}
plot2 <- issue_df %>% filter( open > 0 ) %>%
  ggplot(aes(x=repo, y=open)) + 
  geom_bar(stat="identity", width=.5, fill="blue") + 
  theme(axis.text.x = element_text(angle=90, vjust=0.6))+
  labs(title="Bar Plot",
       subtitle="Summary of count of Language based on repositories")+
       xlab("Repo_Name")+
       ylab("No. of open issues")


plot2

```

### Plot3- Summarizes the count for each language used in Mike's repositories. 

```{r languages}
plot3 <- ggplot(repos_df, aes(language)) + 
  geom_bar() +
  theme_economist()+
  labs(title="Bar Plot",
       subtitle="Summary of count of Language based on repositories")+
  xlab("Language")+
  ylab("Count")
plot3
```

### Plot4- Summarizes the largest repositories by size and language.
The top 3 repositories are spark,	playframework, scala.

```{r pressure}

options(scipen = 999)
plot4 <- repos_df %>%
  filter(size > 20000) %>%
  ggplot(aes(language, size, color = name)) + geom_point() +
  labs(title="Largest repositories by size and language") +
  xlab("Language")+
  ylab("Size")+
  theme_gdocs()+
  scale_color_gdocs()
plot4


```

